### 2020-09-02 Manuscript/pole_table.tex
flip the polarity of Ediacaran poles within the figures and table, add more detail to Ediacaran pole discussion

      Laurentia-Superior(East) &                     Otto Stock dykes and aureole &      B &     279.9 &      48.0 & 227.0 &  69.0 &       4.8 &     2676\$\textasciicircum \{+5\}\$\$\_\{-5\}\$ &                               \textbackslash cite\{Pullaiah1975b\} \\

@@

      Laurentia-Superior(East) &                       Ptarmigan-Mistassini dykes &      B &     287.0 &      54.0 & 213.0 & -45.3 &      13.8 &     2505\$\textasciicircum \{+2\}\$\$\_\{-2\}\$ &                                  \textbackslash cite\{Evans2010a\} \\
      Laurentia-Superior(East) &                               Matachewan dykes R &      A &     278.0 &      48.0 & 238.3 & -44.1 &       1.6 &   2466\$\textasciicircum \{+23\}\$\$\_\{-23\}\$ &                                  \textbackslash cite\{Evans2010a\} \\
      Laurentia-Superior(East) &                               Matachewan dykes N &      A &     278.0 &      48.0 & 239.5 & -52.3 &       2.4 &     2446\$\textasciicircum \{+3\}\$\$\_\{-3\}\$ &                                  \textbackslash cite\{Evans2010a\} \\
               Laurentia-Slave &                                     Malley dykes &      A &     249.8 &      64.2 & 310.0 & -50.8 &       6.7 &     2231\$\textasciicircum \{+2\}\$\$\_\{-2\}\$ &                                 \textbackslash cite\{Buchan2012a\} \\
      Laurentia-Superior(East) &                                 Senneterre dykes &      A &     283.0 &      49.0 & 284.3 & -15.3 &       5.5 &     2218\$\textasciicircum \{+6\}\$\$\_\{-6\}\$ &                                 \textbackslash cite\{Buchan1993a\} \\

@@

               Laurentia-Slave &                                     Dogrib dykes &      A &     245.5 &      62.5 & 315.0 & -31.0 &       7.0 &     2193\$\textasciicircum \{+2\}\$\$\_\{-2\}\$ &                               \textbackslash cite\{Mitchell2014a\} \\
      Laurentia-Superior(East) &                                Biscotasing dykes &      A &     280.0 &      48.0 & 223.9 &  26.0 &       7.0 &     2170\$\textasciicircum \{+3\}\$\$\_\{-3\}\$ &                                  \textbackslash cite\{Evans2010a\} \\
             Laurentia-Wyoming &  Rabbit Creek, Powder River and South Path Dykes &      A &     252.8 &      43.9 & 339.2 &  65.5 &       7.6 &    2160\$\textasciicircum \{+11\}\$\$\_\{-8\}\$ &                                 \textbackslash cite\{Kilian2015a\} \\
               Laurentia-Slave &                                      Indin dykes &      A &     245.6 &      62.5 & 256.0 & -36.0 &       7.0 &    2126\$\textasciicircum \{+3\}\$\$\_\{-18\}\$ &                                 \textbackslash cite\{Buchan2016a\} \\
      Laurentia-Superior(West) &                                 Marathon dykes N &      A &     275.0 &      49.0 & 198.2 &  45.4 &       7.7 &     2124\$\textasciicircum \{+3\}\$\$\_\{-3\}\$ &                                  \textbackslash cite\{Halls2008a\} \\
      Laurentia-Superior(West) &                                 Marathon dykes R &      A &     275.0 &      49.0 & 182.2 &  55.1 &       7.5 &     2104\$\textasciicircum \{+3\}\$\$\_\{-3\}\$ &                                  \textbackslash cite\{Halls2008a\} \\
      Laurentia-Superior(West) &                               Cauchon Lake dykes &      A &     263.0 &      56.0 & 180.9 &  53.8 &       7.7 &     2091\$\textasciicircum \{+2\}\$\$\_\{-2\}\$ &                                  \textbackslash cite\{Evans2010a\} \\
      Laurentia-Superior(West) &                               Fort Frances dykes &      A &     266.0 &      48.0 & 184.6 &  42.8 &       6.1 &     2077\$\textasciicircum \{+5\}\$\$\_\{-5\}\$ &                                  \textbackslash cite\{Evans2010a\} \\
      Laurentia-Superior(East) &                                 Lac Esprit dykes &      A &     282.0 &      53.0 & 170.5 &  62.0 &       6.4 &     2069\$\textasciicircum \{+1\}\$\$\_\{-1\}\$ &                                  \textbackslash cite\{Evans2010a\} \\
      Laurentia-Greenland-Nain &                                  Kangamiut Dykes &      B &     307.0 &      66.0 & 273.8 &  17.1 &       2.7 &   2042\$\textasciicircum \{+12\}\$\$\_\{-12\}\$ &                                 \textbackslash cite\{Fahrig1976b\} \\
               Laurentia-Slave &                                Lac de Gras dykes &      A &     249.6 &      64.4 & 267.9 &  11.8 &       7.1 &     2026\$\textasciicircum \{+5\}\$\$\_\{-5\}\$ &                                 \textbackslash cite\{Buchan2009a\} \\
      Laurentia-Superior(East) &                                      Minto dykes &      A &     285.0 &      57.0 & 171.5 &  38.7 &      13.1 &     1998\$\textasciicircum \{+2\}\$\$\_\{-2\}\$ &                                  \textbackslash cite\{Evans2010a\} \\

@@

@@

@@

      Laurentia-Superior(West) &                              Molson (B+C2) dykes &      A &     262.0 &      55.0 & 218.0 &  28.9 &       3.8 &     1879\$\textasciicircum \{+6\}\$\$\_\{-6\}\$ &                                  \textbackslash cite\{Evans2010a\} \\

@@

@@

                 Laurentia-Rae &                                    Sparrow Dykes &      B &     250.2 &      61.6 & 291.0 &  12.0 &       7.9 &     1827\$\textasciicircum \{+4\}\$\$\_\{-4\}\$ &                                \textbackslash cite\{McGlynn1974a\} \\

@@

@@

@@

                     Laurentia &                                    Cleaver Dykes &      A &     242.0 &      67.5 & 276.7 &  19.4 &       6.1 &     1741\$\textasciicircum \{+5\}\$\$\_\{-5\}\$ &                                 \textbackslash cite\{Irving2004a\} \\
           Laurentia-Greenland &                      Melville Bugt diabase dykes &      B &     303.0 &      74.6 & 273.8 &   5.0 &       8.7 &     1633\$\textasciicircum \{+5\}\$\$\_\{-5\}\$ &                                  \textbackslash cite\{Halls2011a\} \\

@@

@@

@@

@@

                     Laurentia &                               Tobacco Root dykes &      B &     247.6 &      47.4 & 216.1 &   8.7 &      10.5 &   1448\$\textasciicircum \{+49\}\$\$\_\{-49\}\$ &                                 \textbackslash cite\{Harlan2008a\} \\

@@

@@

           Laurentia-Greenland &                    Victoria Fjord dolerite dykes &      B &     315.3 &      81.5 & 231.7 &  10.3 &       4.3 &     1382\$\textasciicircum \{+2\}\$\$\_\{-2\}\$ &                             \textbackslash cite\{Abrahamsen1987a\} \\

@@

           Laurentia-Greenland &                                Kungnat Ring Dyke &      B &     311.7 &      61.2 & 198.7 &   3.4 &       3.2 &     1275\$\textasciicircum \{+2\}\$\$\_\{-2\}\$ &                                  \textbackslash cite\{Piper1977b\} \\

@@

                     Laurentia &                       Mackenzie dykes grand mean &      A &     250.0 &      65.0 & 190.0 &   4.0 &       5.0 &     1267\$\textasciicircum \{+2\}\$\$\_\{-2\}\$ &                                 \textbackslash cite\{Buchan2000a\} \\
           Laurentia-Greenland &                       West Gardar Dolerite Dykes &      B &     311.7 &      61.2 & 201.7 &   8.7 &       6.6 &     1244\$\textasciicircum \{+8\}\$\$\_\{-8\}\$ &                                  \textbackslash cite\{Piper1977b\} \\
           Laurentia-Greenland &                    West Gardar Lamprophyre Dykes &      B &     311.7 &      61.2 & 206.4 &   3.2 &       7.2 &   1238\$\textasciicircum \{+11\}\$\$\_\{-11\}\$ &                                  \textbackslash cite\{Piper1977b\} \\
                     Laurentia &                           Sudbury Dykes Combined &      A &     278.6 &      46.3 & 192.8 &  -2.5 &       2.5 &     1237\$\textasciicircum \{+5\}\$\$\_\{-5\}\$ &                                 \textbackslash cite\{Palmer1977a\} \\

@@

           Laurentia-Greenland &                               Hviddal Giant Dyke &      B &     313.7 &      60.9 & 215.3 &  33.2 &       9.6 &     1184\$\textasciicircum \{+5\}\$\$\_\{-5\}\$ &                                  \textbackslash cite\{Piper1977a\} \\

@@

           Laurentia-Greenland &                               Giant Gabbro Dykes &      B &     313.7 &      60.9 & 226.1 &  42.3 &       9.4 &     1163\$\textasciicircum \{+2\}\$\$\_\{-2\}\$ &                                  \textbackslash cite\{Piper1977a\} \\
           Laurentia-Greenland &                             NE-SW Trending dykes &      B &     314.6 &      61.1 & 230.8 &  33.4 &       5.7 &     1160\$\textasciicircum \{+5\}\$\$\_\{-5\}\$ &                                  \textbackslash cite\{Piper1992a\} \\
                     Laurentia &                        Ontario lamprophyre dykes &     NR &     273.3 &      48.8 & 223.3 &  58.0 &       9.2 &   1143\$\textasciicircum \{+10\}\$\$\_\{-10\}\$ &                                 \textbackslash cite\{Piispa2018a\} \\
                     Laurentia &                                    Abitibi Dykes &      A &     279.0 &      48.0 & 215.5 &  48.8 &      14.1 &     1141\$\textasciicircum \{+2\}\$\$\_\{-2\}\$ &                                  \textbackslash cite\{Ernst1993a\} \\

@@

@@

@@

@@

                     Laurentia &                                  Gunbarrel dykes &      B &     248.7 &      44.8 & 138.2 &   9.1 &      12.0 &      778\$\textasciicircum \{+2\}\$\$\_\{-2\}\$ &  Calculation from \textbackslash cite\{Eyster2019a\} based on d... \\

@@

                     Laurentia &                                 Long Range Dykes &      B &     303.3 &      53.7 & 355.3 &  19.0 &      17.4 &      615\$\textasciicircum \{+2\}\$\$\_\{-2\}\$ &                                 \textbackslash cite\{Murthy1992a\} \\
                     Laurentia &                         Baie des Moutons complex &      B &     301.0 &      50.8 & 332.7 &  42.6 &      12.0 &      583\$\textasciicircum \{+2\}\$\$\_\{-2\}\$ &                             \textbackslash cite\{McCausland2011a\} \\
                     Laurentia &                         Baie des Moutons complex &      B &     301.0 &      50.8 & 321.5 & -34.2 &      15.4 &      583\$\textasciicircum \{+2\}\$\$\_\{-2\}\$ &                             \textbackslash cite\{McCausland2011a\} \\
                     Laurentia &                       Callander Alkaline Complex &      B &     280.6 &      46.2 & 301.4 &  46.3 &       6.0 &      575\$\textasciicircum \{+5\}\$\$\_\{-5\}\$ &                                 \textbackslash cite\{Symons1991a\} \\
                     Laurentia &                                 Catoctin Basalts &      B &     281.8 &      38.5 & 296.7 &  42.0 &      17.5 &      572\$\textasciicircum \{+5\}\$\$\_\{-5\}\$ &                                  \textbackslash cite\{Meert1994a\} \\
                     Laurentia &                      Sept-Iles layered intrusion &      B &     293.5 &      50.2 & 321.0 & -20.0 &       6.7 &      565\$\textasciicircum \{+4\}\$\$\_\{-4\}\$ &                                \textbackslash cite\{Tanczyk1987a\} \\

>>>>

  Baltica-Fennoscandia-Karelia &                                Koitere sanukitoids &      B &      30.6 &      63.3 & 192.5 & -67.5 &      19.5 &     2684\$\textasciicircum \{+2\}\$\$\_\{-2\}\$ &                                                NaN \\
      Laurentia-Superior(East) &                       Otto Stock dikes and aureole &      B &     279.9 &      48.0 & 227.0 &  69.0 &       4.8 &     2676\$\textasciicircum \{+5\}\$\$\_\{-5\}\$ &                               \textbackslash cite\{Pullaiah1975b\} \\

@@

          Baltica-Fennoscandia &                   Shalskiy thick gabbronorite dike &      B &      36.0 &      61.9 & 222.1 &  22.7 &      11.5 &     2511\$\textasciicircum \{+2\}\$\$\_\{-2\}\$ &                                                NaN \\
      Laurentia-Superior(East) &                         Ptarmigan-Mistassini dikes &      B &     287.0 &      54.0 & 213.0 & -45.3 &      13.8 &     2505\$\textasciicircum \{+2\}\$\$\_\{-2\}\$ &                                  \textbackslash cite\{Evans2010a\} \\
          Baltica-Fennoscandia &                     Generalskaya Layered Intrusion &      B &      31.0 &      69.4 & 292.7 & -42.5 &      10.4 &     2505\$\textasciicircum \{+2\}\$\$\_\{-2\}\$ &                                                NaN \\
          Baltica-Fennoscandia &                              Monchegorsk Intrusion &      B &      33.0 &      68.0 & 265.3 &   1.3 &       9.9 &     2504\$\textasciicircum \{+2\}\$\$\_\{-2\}\$ &                                                NaN \\
          Baltica-Fennoscandia &  Avdeev gabbronorite and thin Shalskiy diabase ... &      B &      36.0 &      61.9 & 243.5 & -12.3 &      14.0 &   2476\$\textasciicircum \{+35\}\$\$\_\{-35\}\$ &                                                NaN \\
      Laurentia-Superior(East) &                                 Matachewan dikes R &      A &     278.0 &      48.0 & 238.3 & -44.1 &       1.6 &   2466\$\textasciicircum \{+23\}\$\$\_\{-23\}\$ &                                  \textbackslash cite\{Evans2010a\} \\
          Baltica-Fennoscandia &                          Imandra Layered Intrusion &      B &      33.1 &      67.6 & 280.3 & -16.1 &       7.8 &   2446\$\textasciicircum \{+39\}\$\$\_\{-39\}\$ &                                                NaN \\
          Baltica-Fennoscandia &                                     Karelian dikes &      B &      30.7 &      66.0 & 278.7 & -19.9 &       6.1 &     2446\$\textasciicircum \{+5\}\$\$\_\{-5\}\$ &                                                NaN \\
      Laurentia-Superior(East) &                                 Matachewan dikes N &      A &     278.0 &      48.0 & 239.5 & -52.3 &       2.4 &     2446\$\textasciicircum \{+3\}\$\$\_\{-3\}\$ &                                  \textbackslash cite\{Evans2010a\} \\
          Baltica-Fennoscandia &                            Taivalkoski 2.3 Ga dike &     C+ &      28.1 &      65.5 & 257.3 &  20.4 &       6.3 &   2339\$\textasciicircum \{+18\}\$\$\_\{-18\}\$ &                                                NaN \\
               Laurentia-Slave &                                       Malley dikes &      A &     249.8 &      64.2 & 310.0 & -50.8 &       6.7 &     2231\$\textasciicircum \{+2\}\$\$\_\{-2\}\$ &                                 \textbackslash cite\{Buchan2012a\} \\
      Laurentia-Superior(East) &                                   Senneterre dikes &      A &     283.0 &      49.0 & 284.3 & -15.3 &       5.5 &     2218\$\textasciicircum \{+6\}\$\$\_\{-6\}\$ &                                 \textbackslash cite\{Buchan1993a\} \\

@@

               Laurentia-Slave &                                       Dogrib dikes &      A &     245.5 &      62.5 & 315.0 & -31.0 &       7.0 &     2193\$\textasciicircum \{+2\}\$\$\_\{-2\}\$ &                               \textbackslash cite\{Mitchell2014a\} \\
      Laurentia-Superior(East) &                                  Biscotasing dikes &      A &     280.0 &      48.0 & 223.9 &  26.0 &       7.0 &     2170\$\textasciicircum \{+3\}\$\$\_\{-3\}\$ &                                  \textbackslash cite\{Evans2010a\} \\
             Laurentia-Wyoming &    Rabbit Creek, Powder River and South Path dikes &      A &     252.8 &      43.9 & 339.2 &  65.5 &       7.6 &    2160\$\textasciicircum \{+11\}\$\$\_\{-8\}\$ &                                 \textbackslash cite\{Kilian2015a\} \\
               Laurentia-Slave &                                        Indin dikes &      A &     245.6 &      62.5 & 256.0 & -36.0 &       7.0 &    2126\$\textasciicircum \{+3\}\$\$\_\{-18\}\$ &                                 \textbackslash cite\{Buchan2016a\} \\
      Laurentia-Superior(West) &                                   Marathon dikes N &      A &     275.0 &      49.0 & 198.2 &  45.4 &       7.7 &     2124\$\textasciicircum \{+3\}\$\$\_\{-3\}\$ &                                  \textbackslash cite\{Halls2008a\} \\
      Laurentia-Superior(West) &                                   Marathon dikes R &      A &     275.0 &      49.0 & 182.2 &  55.1 &       7.5 &     2104\$\textasciicircum \{+3\}\$\$\_\{-3\}\$ &                                  \textbackslash cite\{Halls2008a\} \\
      Laurentia-Superior(West) &                                 Cauchon Lake dikes &      A &     263.0 &      56.0 & 180.9 &  53.8 &       7.7 &     2091\$\textasciicircum \{+2\}\$\$\_\{-2\}\$ &                                  \textbackslash cite\{Evans2010a\} \\
      Laurentia-Superior(West) &                                 Fort Frances dikes &      A &     266.0 &      48.0 & 184.6 &  42.8 &       6.1 &     2077\$\textasciicircum \{+5\}\$\$\_\{-5\}\$ &                                  \textbackslash cite\{Evans2010a\} \\
      Laurentia-Superior(East) &                                   Lac Esprit dikes &      A &     282.0 &      53.0 & 170.5 &  62.0 &       6.4 &     2069\$\textasciicircum \{+1\}\$\$\_\{-1\}\$ &                                  \textbackslash cite\{Evans2010a\} \\
              Baltica-Sarmatia &               Volyn-Dniestr-Bug intrusions A-group &      B &      29.8 &      49.6 & 182.9 &  15.7 &      13.7 &   2061\$\textasciicircum \{+20\}\$\$\_\{-20\}\$ &                                                NaN \\
          Baltica-Fennoscandia &                               Kuetsyarvi Formation &      B &      29.5 &      69.5 & 300.8 &  24.7 &      16.4 &     2060\$\textasciicircum \{+8\}\$\$\_\{-8\}\$ &                                                NaN \\
      Laurentia-Greenland-Nain &                                    Kangamiut dikes &      B &     307.0 &      66.0 & 273.8 &  17.1 &       2.7 &   2042\$\textasciicircum \{+12\}\$\$\_\{-12\}\$ &                                 \textbackslash cite\{Fahrig1976b\} \\
               Laurentia-Slave &                                  Lac de Gras dikes &      A &     249.6 &      64.4 & 267.9 &  11.8 &       7.1 &     2026\$\textasciicircum \{+5\}\$\$\_\{-5\}\$ &                                 \textbackslash cite\{Buchan2009a\} \\
              Baltica-Sarmatia &                       Volyn-Dniestr-Bug intrusions &      B &      27.4 &      50.9 & 140.4 &  64.4 &      12.7 &   2000\$\textasciicircum \{+10\}\$\$\_\{-10\}\$ &                                                NaN \\
      Laurentia-Superior(East) &                                        Minto dikes &      A &     285.0 &      57.0 & 171.5 &  38.7 &      13.1 &     1998\$\textasciicircum \{+2\}\$\$\_\{-2\}\$ &                                  \textbackslash cite\{Evans2010a\} \\
             Baltica - Karelia &                           Onego 1975 Ma Intrusions &      A &      34.0 &      62.1 & 101.5 &  44.4 &       6.3 &     1976\$\textasciicircum \{+9\}\$\$\_\{-9\}\$ &                                                NaN \\
          Baltica-Fennoscandia &                                    Konchozero Sill &      B &      34.0 &      62.1 & 281.9 & -14.2 &      10.4 &   1974\$\textasciicircum \{+27\}\$\$\_\{-27\}\$ &                                                NaN \\

@@

          Baltica-Fennoscandia &             Tsuomasavarri Gabbro-Diorite Intrusion &      B &      28.3 &      69.9 & 247.3 &  40.2 &       6.0 &     1931\$\textasciicircum \{+2\}\$\$\_\{-2\}\$ &                                                NaN \\

@@

          Baltica-Fennoscandia &                         Kiuruvesi-Pielavesi gabbro &      B &      26.8 &      63.2 & 231.3 &  41.1 &       5.4 &     1886\$\textasciicircum \{+6\}\$\$\_\{-5\}\$ &                                                NaN \\

@@

      Laurentia-Superior(West) &                                Molson (B+C2) dikes &      A &     262.0 &      55.0 & 218.0 &  28.9 &       3.8 &     1879\$\textasciicircum \{+6\}\$\$\_\{-6\}\$ &                                  \textbackslash cite\{Evans2010a\} \\

@@

        Baltica - Fennoscandia &                                      Keuruu dikes  &     B  &      24.7 &      62.3 & 230.9 &  45.7 &       5.5 &   1869\$\textasciicircum \{+10\}\$\$\_\{-10\}\$ &                                                NaN \\

@@

                 Laurentia-Rae &                                      Sparrow dikes &      B &     250.2 &      61.6 & 291.0 &  12.0 &       7.9 &     1827\$\textasciicircum \{+4\}\$\$\_\{-4\}\$ &                                \textbackslash cite\{McGlynn1974a\} \\

@@

          Baltica-Fennoscandia &                                    Notträsk gabbro &      B &      21.8 &      65.8 & 216.2 &  43.5 &       6.1 &     1806\$\textasciicircum \{+6\}\$\$\_\{-6\}\$ &                                                NaN \\
          Baltica-Fennoscandia &                                      Kallax gabbro &      B &      22.0 &      65.5 & 209.0 &  49.0 &       nan &     1800\$\textasciicircum \{+5\}\$\$\_\{-6\}\$ &                                                NaN \\
          Baltica-Fennoscandia &                 Lake Ladoga, Mean intr. \& dikes, A &      B &      30.0 &      61.3 & 229.1 &  50.9 &       nan &   1800\$\textasciicircum \{+19\}\$\$\_\{-56\}\$ &                                                NaN \\
          Baltica-Fennoscandia &                                      Hoting gabbro &      A &      16.2 &      64.2 & 233.3 &  43.0 &      10.9 &   1786\$\textasciicircum \{+10\}\$\$\_\{-10\}\$ &                                                NaN \\

@@

          Baltica-Fennoscandia &                              Småland intrusives -C &      A &      15.7 &      57.1 & 182.7 &  45.7 &       8.0 &     1777\$\textasciicircum \{+8\}\$\$\_\{-8\}\$ &                                                NaN \\
          Baltica-Fennoscandia &                                 Shoksha Sandstones &      B &      33.8 &      61.3 & 221.1 &  39.7 &       4.0 &   1775\$\textasciicircum \{+25\}\$\$\_\{-25\}\$ &                                                NaN \\

@@

              Baltica-Sarmatia &                       Volyn-Dniestr-Bug intrusions &      A &      28.6 &      50.6 & 169.1 &  26.5 &       3.9 &   1755\$\textasciicircum \{+15\}\$\$\_\{-15\}\$ &                                                NaN \\
          Baltica-Fennoscandia &                                MEAN Ropruchey sill &      B &      35.3 &      61.4 & 217.0 &  39.1 &       8.6 &     1751\$\textasciicircum \{+3\}\$\$\_\{-3\}\$ &                                                NaN \\
                     Laurentia &                                      Cleaver dikes &      A &     242.0 &      67.5 & 276.7 &  19.4 &       6.1 &     1741\$\textasciicircum \{+5\}\$\$\_\{-5\}\$ &                                 \textbackslash cite\{Irving2004a\} \\
              Baltica-Sarmatia &                       Volyn-Dniestr-Bug intrusions &      B &      29.6 &      50.0 & 163.2 &  10.7 &      10.2 &   1722\$\textasciicircum \{+12\}\$\$\_\{-12\}\$ &                                                NaN \\
        Baltica - Fennoscandia &                                   Häme dike swarm  &      B &      25.1 &      61.4 & 209.8 &  23.6 &      14.7 &   1647\$\textasciicircum \{+14\}\$\$\_\{-14\}\$ &                                                NaN \\
                       Baltica &                        Sipoo Quartz Porphyry dikes &      B &      25.3 &      60.3 & 180.4 &  26.4 &       9.4 &   1633\$\textasciicircum \{+10\}\$\$\_\{-10\}\$ &                                                NaN \\
           Laurentia-Greenland &                        Melville Bugt diabase dikes &      B &     303.0 &      74.6 & 273.8 &   5.0 &       8.7 &     1633\$\textasciicircum \{+5\}\$\$\_\{-5\}\$ &                                  \textbackslash cite\{Halls2011a\} \\
                       Baltica &                              Quartz porphyry dikes &      B &      26.8 &      61.3 & 175.4 &  30.2 &       9.4 &   1631\$\textasciicircum \{+10\}\$\$\_\{-10\}\$ &                                                NaN \\
                       Baltica &                                 Hoting basic dikes &      B &      16.2 &      64.2 & 146.7 &  21.9 &      13.7 &   1614\$\textasciicircum \{+24\}\$\$\_\{-24\}\$ &                                                NaN \\

@@

                       Baltica &                                   Åland dike swarm &      A &      20.0 &      60.0 & 191.4 &  23.7 &       2.8 &   1578\$\textasciicircum \{+12\}\$\$\_\{-12\}\$ &                                                NaN \\
                       Baltica &                            Satakunta dike swarm -C &      A &      21.5 &      62.0 & 188.1 &  29.3 &       6.6 &   1578\$\textasciicircum \{+12\}\$\$\_\{-12\}\$ &                                                NaN \\
                       Baltica &                                  Ragunda Formation &      B &      16.1 &      63.3 & 166.6 &  51.6 &       7.1 &   1506\$\textasciicircum \{+13\}\$\$\_\{-13\}\$ &                                                NaN \\

@@

                       Baltica &                           MEAN Bunkris/Glysjon/Oje &      B &      13.5 &      61.5 & 179.8 &  28.3 &      13.2 &     1469\$\textasciicircum \{+9\}\$\$\_\{-9\}\$ &                                                NaN \\

@@

                       Baltica &                    Lake Ladoga basalt, sill, dikes &      A &      31.2 &      61.5 & 177.1 &  15.2 &       5.5 &   1452\$\textasciicircum \{+12\}\$\$\_\{-12\}\$ &                                                NaN \\

@@

                     Laurentia &                                 Tobacco Root dikes &      B &     247.6 &      47.4 & 216.1 &   8.7 &      10.5 &   1448\$\textasciicircum \{+49\}\$\$\_\{-49\}\$ &                                 \textbackslash cite\{Harlan2008a\} \\

@@

           Laurentia-Greenland &                      Victoria Fjord dolerite dikes &      B &     315.3 &      81.5 & 231.7 &  10.3 &       4.3 &     1382\$\textasciicircum \{+2\}\$\$\_\{-2\}\$ &                             \textbackslash cite\{Abrahamsen1987a\} \\

@@

                       Baltica &                                             Mashak &      B &      57.0 &      54.0 & 193.0 &   1.8 &      14.8 &   1376\$\textasciicircum \{+10\}\$\$\_\{-10\}\$ &                                                NaN \\

@@

@@

           Laurentia-Greenland &                                  Kungnat Ring dike &      B &     311.7 &      61.2 & 198.7 &   3.4 &       3.2 &     1275\$\textasciicircum \{+2\}\$\$\_\{-2\}\$ &                                  \textbackslash cite\{Piper1977b\} \\
                     Laurentia &                         Mackenzie dikes grand mean &      A &     250.0 &      65.0 & 190.0 &   4.0 &       5.0 &     1267\$\textasciicircum \{+2\}\$\$\_\{-2\}\$ &                                 \textbackslash cite\{Buchan2000a\} \\
                       Baltica &                       MEAN post-Jotnian intrusions &      A &      18.1 &      62.4 & 159.1 &  -1.8 &       3.4 &   1258\$\textasciicircum \{+12\}\$\$\_\{-12\}\$ &                                                NaN \\
           Laurentia-Greenland &                         West Gardar Dolerite dikes &      B &     311.7 &      61.2 & 201.7 &   8.7 &       6.6 &     1244\$\textasciicircum \{+8\}\$\$\_\{-8\}\$ &                                  \textbackslash cite\{Piper1977b\} \\
           Laurentia-Greenland &                      West Gardar Lamprophyre dikes &      B &     311.7 &      61.2 & 206.4 &   3.2 &       7.2 &   1238\$\textasciicircum \{+11\}\$\$\_\{-11\}\$ &                                  \textbackslash cite\{Piper1977b\} \\
                     Laurentia &                             Sudbury dikes Combined &      A &     278.6 &      46.3 & 192.8 &  -2.5 &       2.5 &     1237\$\textasciicircum \{+5\}\$\$\_\{-5\}\$ &                                 \textbackslash cite\{Palmer1977a\} \\

@@

           Laurentia-Greenland &                                 Hviddal Giant dike &      B &     313.7 &      60.9 & 215.3 &  33.2 &       9.6 &     1184\$\textasciicircum \{+5\}\$\$\_\{-5\}\$ &                                  \textbackslash cite\{Piper1977a\} \\

@@

           Laurentia-Greenland &                                 Giant Gabbro dikes &      B &     313.7 &      60.9 & 226.1 &  42.3 &       9.4 &     1163\$\textasciicircum \{+2\}\$\$\_\{-2\}\$ &                                  \textbackslash cite\{Piper1977a\} \\
           Laurentia-Greenland &                               NE-SW Trending dikes &      B &     314.6 &      61.1 & 230.8 &  33.4 &       5.7 &     1160\$\textasciicircum \{+5\}\$\$\_\{-5\}\$ &                                  \textbackslash cite\{Piper1992a\} \\
                     Laurentia &                          Ontario lamprophyre dikes &     NR &     273.3 &      48.8 & 223.3 &  58.0 &       9.2 &   1143\$\textasciicircum \{+12\}\$\$\_\{-12\}\$ &                                 \textbackslash cite\{Piispa2018a\} \\
                     Laurentia &                                      Abitibi dikes &      A &     279.0 &      48.0 & 215.5 &  48.8 &      14.1 &     1141\$\textasciicircum \{+2\}\$\$\_\{-2\}\$ &                                  \textbackslash cite\{Ernst1993a\} \\
                       Baltica &                        Salla dike (width 60-100 m) &      B &      28.8 &      66.8 & 111.6 &  70.6 &       8.1 &     1122\$\textasciicircum \{+5\}\$\$\_\{-3\}\$ &                                                NaN \\

@@

                       Baltica &                             MEAN Bamble Intrusions &     C+ &       9.5 &      58.9 & 222.5 & -15.1 &      19.3 &   1048\$\textasciicircum \{+73\}\$\$\_\{-73\}\$ &                                                NaN \\
                       Baltica &                           Laanila-Ristijarvi dikes &      B &      28.1 &      68.7 & 212.2 &  -2.1 &      13.8 &   1044\$\textasciicircum \{+52\}\$\$\_\{-52\}\$ &                                                NaN \\

@@

                       Baltica &                            MEAN Blekinga dolerites &      B &      15.0 &      56.1 & 247.0 &  13.0 &      16.0 &      950\$\textasciicircum \{+4\}\$\$\_\{-4\}\$ &                                                NaN \\
                       Baltica &               dikes of central and southern Sweden &      A &      14.2 &      58.4 & 240.7 &  -0.9 &       6.7 &    945\$\textasciicircum \{+10\}\$\$\_\{-10\}\$ &                                                NaN \\

@@

        Baltica - Fennoscandia &                Bjerkreim-Sokndal layered intrusion &      B &       6.1 &      58.5 & 217.9 & -35.9 &       6.3 &    921\$\textasciicircum \{+17\}\$\$\_\{-17\}\$ &                                                NaN \\
                       Baltica &                    Bratton and Algon Igneous Rocks &      B &      11.7 &      57.9 & 249.0 &   5.0 &       3.9 &    916\$\textasciicircum \{+11\}\$\$\_\{-11\}\$ &                                                NaN \\
                       Baltica &                           MEAN Rogaland igneous cx &      B &       6.9 &      58.3 & 207.9 & -43.2 &      10.1 &    903\$\textasciicircum \{+33\}\$\$\_\{-33\}\$ &                                                NaN \\
                       Baltica &                                   Hunnedalen dikes &      B &       7.0 &      58.9 & 222.0 & -41.0 &      15.6 &    848\$\textasciicircum \{+27\}\$\$\_\{-27\}\$ &                                                NaN \\

@@

                       Baltica &                                    Katav Formation &      B &      57.4 &      54.8 & 169.9 &  35.7 &      11.4 &  800\$\textasciicircum \{+100\}\$\$\_\{-100\}\$ &                                                NaN \\
                     Laurentia &                                    Gunbarrel dikes &      B &     248.7 &      44.8 & 138.2 &   9.1 &      12.0 &      778\$\textasciicircum \{+2\}\$\$\_\{-2\}\$ &  Calculation from \textbackslash cite\{Eyster2019a\} based on d... \\

@@

                       Baltica &                                     Egersund dikes &      A &       5.9 &      58.8 &  44.1 &  31.4 &      15.6 &      616\$\textasciicircum \{+3\}\$\$\_\{-3\}\$ &                                                NaN \\
                     Laurentia &                                   Long Range dikes &      B &     303.3 &      53.7 & 175.3 & -19.0 &      17.4 &      615\$\textasciicircum \{+2\}\$\$\_\{-2\}\$ &                                 \textbackslash cite\{Murthy1992a\} \\
                     Laurentia &                           Baie des Moutons complex &      B &     301.0 &      50.8 & 152.7 & -42.6 &      12.0 &      583\$\textasciicircum \{+2\}\$\$\_\{-2\}\$ &                             \textbackslash cite\{McCausland2011a\} \\
                     Laurentia &                           Baie des Moutons complex &      B &     301.0 &      50.8 & 141.5 &  34.2 &      15.4 &      583\$\textasciicircum \{+2\}\$\$\_\{-2\}\$ &                             \textbackslash cite\{McCausland2011a\} \\
                     Laurentia &                         Callander Alkaline Complex &      B &     280.6 &      46.2 & 121.4 & -46.3 &       6.0 &      575\$\textasciicircum \{+5\}\$\$\_\{-5\}\$ &                                 \textbackslash cite\{Symons1991a\} \\
                     Laurentia &                                   Catoctin Basalts &      B &     281.8 &      38.5 & 116.7 & -42.0 &      17.5 &      572\$\textasciicircum \{+5\}\$\$\_\{-5\}\$ &                                  \textbackslash cite\{Meert1994a\} \\
                       Baltica &                                       Volhyn lavas &      B &      26.0 &      51.2 &   4.4 &  19.8 &      28.3 &    571\$\textasciicircum \{+10\}\$\$\_\{-10\}\$ &                                                NaN \\
                     Laurentia &                        Sept-Iles layered intrusion &      B &     293.5 &      50.2 & 141.0 &  20.0 &       6.7 &      565\$\textasciicircum \{+4\}\$\$\_\{-4\}\$ &                                \textbackslash cite\{Tanczyk1987a\} \\
                       Baltica &                               Kurgashlya formation &      A &      57.5 &      53.3 & 314.5 &  50.9 &       5.3 &      565\$\textasciicircum \{+5\}\$\$\_\{-5\}\$ &                                                NaN \\
                       Baltica &                                  Bakeevo formation &      A &      58.2 &      54.9 & 299.1 &  42.3 &       5.3 &      565\$\textasciicircum \{+5\}\$\$\_\{-5\}\$ &                                                NaN \\
                       Baltica &                        Basu-Kukkarauk formation -C &      B &      57.0 &      54.0 & 187.3 &   1.1 &       5.8 &      562\$\textasciicircum \{+5\}\$\$\_\{-5\}\$ &                                                NaN \\
